### 2017-05-25 scheduling/article/article.tex
Fixed bug related with table

			\begin{table}[h]
				\centering
				\begin{tabu}{ | c | c | p{.58\linewidth} |}
					\hline
					\bfseries Modelo & \bfseries Retraso & \bfseries Programación
					\csvreader[head to column names]{../results/csv/sched_200_1.csv}{}
					{\\\hline\model&\delay&\schedule}
					\\\hline
				\end{tabu}
				\caption{[TODO ]}
				\label{table:sol-sched_200_1}
			\end{table}

>>>>

			\csvreader[
			  longtable= | c | c | p{.58\linewidth} |,
			  table head=\hline \bfseries Modelo & \bfseries Retraso & \bfseries Programación \\ \hline \endhead,
  			table foot= \caption{[TODO ]}\label{table:sol-sched_200_1}\\,
				late after line=\\\hline,
  			before reading={\catcode`\#=12},after reading={\catcode`\#=6}
			]{../results/csv/sched_200_1.csv}{1=\model,2=\delay,3=\schedule}{\model&\delay&\schedule}
